Accurate binding of sodium and calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-11-14 Manuscript/manuscript.tex
Changed title methods subsection to be more accurate

\subsection{Validation of lipid bilayer structure against experiments}
The structures of lipid bilayers in simulations without ions were validated against NMR by calculating the order parameters for the C-H bonds and \mbox{x-ray} scattering experiments by the scattering form factors. NMR order parameters validate the structures sampled by the individual lipid molecules with atomic resolution. The simulated order parameters were calculated for all C-H bonds in lipid molecules from Eq. \ref{OP}. Scattering form factors validate the dimensions of the lipid bilayer (e.g., thickness and area per molecule). Form factors were calculated using

>>>>

\subsection{Validation of lipid bilayer structure against NMR and scattering experiments}
The structures of lipid bilayers in simulations without ions were validated against NMR by calculating the order parameters for the C-H bonds and \mbox{x-ray} scattering experiments by the scattering form factors. NMR order parameters validate the structures sampled by the individual lipid molecules with atomic resolution. The simulated order parameters were calculated for all C-H bonds in lipid molecules from Eq. \ref{OP}. Scattering form factors validate the dimensions of the lipid bilayer (e.g., thickness and area per molecule). Form factors were calculated using
